### 2018-01-10 ident/docs/ident_manuscript.tex
expanded explanation for figure 1 in results

\subsection{Variability in the degree of identifiability of each parameter:}
We found that the ability of a combination of experiments to identify a particular parameter widely varies depending the the position of the flux in the metabolic network with respect to the inputs and the outputs of the network. In Figure \ref{fig:figure1} we show the number of combinations of experiments that are capable of identifying each parameter in each flux. In the left panels (Figure \ref{fig:figure1}a-c), the data is show when noise-free data is used for identification. The identifiability information for parameters using data with additive noise is shown on the right panel (Figure \ref{fig:figure1}d-f).

>>>>

\subsection{Variability in the degree of identifiability of each parameter:}
In Figure \ref{fig:figure1} we show the number of combinations of experiments that are capable of identifying each parameter in each flux. In the left panels (Figure \ref{fig:figure1}a-c), the data is shown when noise-free data is used for identification. The identifiability information for parameters using data with additive noise is shown on the right panel (Figure \ref{fig:figure1}d-f). As seen in these figures, irrespective of the presence or absence of noise in the data, the number of combinations that can identify each parameter varies widely, even for parameters within the same flux.

Since both fluxes $v_1$ and $v_2$ are represented by the same enzyme kinetic rate law, we compare the number of data combinations that are capable of identifying the different parameters used to model these fluxes. We observe that the number of data combinations identifying the maximum reaction rates ($V_i^{max}$) for both $v_1$ (Figure \ref{fig:figure1}a and d) and $v_2$ (Figure \ref{fig:figure1}b and e) is always greater for than the number of data combinations that identify the enzyme binding ($K_i$) constants for both of these fluxes, irrespective of the presence of noise in the experimental data.

Although, only about 20\% of the 4896 different data combinations can identify parameters in $v_1$, the difference between the number of data combinations being able to identify the different parameters in $v_1$ is less than 2\% (Figure \ref{fig:figure1}a and d). However, the same could not be said for the number of data combinations identifying parameters in $v_2$. In contrast to the high number of data combinations identifying $V_2^{max}$ (89.5\%), less than 2\% of the combinations are able to identify $K_2^{pep}$ (Figure \ref{fig:figure1}b and e).

The trend noted earlier for $v_1$ and $v_2$ with regards to the number of data combinations identifying the reaction rate parameters versus the number of data sets identifying the corresponding enzyme binding constants in these fluxes is also seen for $v_3$, i.e., the percentage of data combinations identifying $V_3^{max} (1)$ and $V_3^{max}(2)$ is greater than the percentage of combinations that can identify $K_3^{fdp}(1)$ and $K_3^{fdp}(2)$.

We found that the ability of a combination of experiments to identify a particular parameter widely varies depending the the position of the flux in the metabolic network with respect to the inputs and the outputs of the network.

As seen from Figure \ref{fig:figure1},
